Follow-up Samples

### 2017-04-12 submission/supplemental.Rmd
try to fit table on one page (not possible)

\newpage
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

@@

**Table S2: Summary of OTUs in Adenoma, Advanced Adenoma, and Carcinoma Models**

@@

# Create selection vector
common_vars <- common_vars_summary$otu

@@

st2 <- select(common_vars_summary, otu) %>% 
  mutate(Tax = gsub("_unclassified", "", common_vars_summary$lowest_ID)) %>% 
  mutate(adn_MDA = adn_MDA$median_MDA, srn_MDA = srn_MDA$median_MDA, crc_MDA = crc_MDA$median_MDA) %>% 
  arrange(desc(adn_MDA), desc(srn_MDA), desc(crc_MDA))

colnames(st2) <- c("OTU", "Lowest Taxonomic ID", "Adenoma Model MDA", "SRN Model MDA", "Carcinoma Model MDA")

kable(st2, format = "markdown", align = 'c', padding = 2)

>>>>

\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

@@

**Table S2: Summary of Common OTUs for All Diagnosis Groups**

@@

# Create selection vector
common_vars <- common_vars_summary$otu
common_num <- as.numeric(gsub("Otu", "", common_vars_summary$otu))

@@

st2 <- select(common_vars_summary, otu) %>% 
  mutate(Tax = gsub("_unclassified", "", common_vars_summary$lowest_ID)) %>% 
  mutate(otu = paste("OTU", common_num, sep = "")) %>% 
  mutate(adn_MDA = round(adn_MDA$median_MDA, digits = 2), srn_MDA = round(srn_MDA$median_MDA, digits = 2), crc_MDA = round(crc_MDA$median_MDA, digits = 2)) %>% 
  arrange(desc(adn_MDA), desc(srn_MDA), desc(crc_MDA))

colnames(st2) <- c("OTU", "Lowest Taxonomic ID", "Adenoma Median MDA", "Advanced Adenoma Median MDA", "Carcinoma Median MDA")

kable(st2, format = "markdown", align = 'c', padding = 0)
